\TheTitle

### 2016-04-26 linvis.tex
Minor capitalization changes

        With an average of more than 900 top-level merges into the Linux kernel per
        release, many containing hundreds of commits and some containing thousands,
        maintenance of older versions of the kernel becomes nearly impossible.
        Various commercial products, such as the Android platform, run older
        versions of the kernel. Due to security, performance, and changing hardware
        needs, maintainers must understand what changes (commits) are added the current version of the kernel
        since the last time they inspected it in order to make the necessary
        patches.

        Current tools provide information about repositories through the directed
        acyclic graph (DAG) of the repostory, which is helpful for smaller projects. However, with
        the scale and number of branches in the kernel the DAG becomes overwhelming
        very quickly. Furthermore, the DAG contains every ancestor of every commit, while maintainers are
        more interested in how and when a commmit arrives to Linux official repository.

        In this paper, we present \tool, a tool that uses a tree-based model to construct a clearer summary of the changes made. \tool is designed to allow
        users to explore the topology of the repository for a given release of the kernel and view an aggregated summary of the changes made.

@@

\evantodo {
        \begin{enumerate}
                \item Add simplified abstract -- From email
                \item replace figure reference with Figure~\\ref
                \item Check captions
                \item gitk to Gitk
                \item git to Git
                \item diff to patch
                \item id to ID
                \item Master to master
        \end{enumerate}
}

Between 50 and 70 thousand commits are added to the Linux kernel per version
requiring maintainers of older versions of the Linux kernel to sift through
thousands of commits and merges with tools that are unable to filter and effectively
visualize projects at the scale of the kernel. Older versions of the kernel are used
in embedded systems and mobile phones; for security purposes, performance needs, and
changing hardware requirements, maintainers must be able to understand the changes
being made in the current version of the kernel in order to produce the necessary
patches for the older versions of the kernel. Tools like Gitk use a directed acyclic
graph (DAG) model of the repository, showing all commits and merges in chronological
order by when the commit was authored, not by when it arrived in the official Linux
repository.

This representation works in smaller projects; it enables users to see when changes
are made, when these changes are merged, how each branch is interacting, and the
point where a branch forks from the master branch. In large modular projects, like
the Linux kernel, the DAG becomes a mess of merges and commits (figure
\ref{fig:gitk}) losing its visual meaning. In some cases, the Linux kernel is simply
too large for the system to generate a visualization; Github provides a DAG view for
many projects, but is unable to display the visualization for projects at the scale
of the Linux of the kernel (figure \ref{fig:gitfail}).  Between 60 and 70k new
commits are created for the Linux project every year; According to our previous
work\cite{German2015}, a commit takes a median of 30 days from the time it is
authored until it arrives in the official repository. The snapshot of the kernel
tomorrow may be different than the snapshot from today, containing new commits
authored in the past; distinguishing these new commits from the commits in the
snapshot from today is not trivial.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitk.png}
        \caption{A sample DAG view of commits from Linux in Gitk. Commits point
                towards their ancestors, and there is no clear indication of the way
                the travel to reach Master. In fact, neither Gitk nor git is capable
                of showing what commits were done in master.}
        \label{fig:gitk}
\end{figure}

@@

Git uses a directed acyclic graph (DAG) as its main data model. In this model, a
commit has one or more ordered parents (ancestors), except the root commits of a
repository which do not have ancestors--Linux git repository has two such commits.
Commits are divided into merge commits, merging two or more branches, and non-merge
commits. Non-merge commits have only one parent, while merge commits have two or
more. The order of the parents matter: the first parent is the branch in which the
merge is being done, while the rest indicate the branches being merged (git allows
merging multiple branches simultaneously). The second parent is the first branch
merged, the third parent is the second branched merged.

Once a commit is created, it is never changed. Git allows operations to alter
commits or reorder them, but it changes the commit id in the process, effectively
making a new commit. This makes commits unable to record the traversal of merges
from the commit to the merge into the master branch.

A short example: assume the of commits represented in figure \ref{fig:repoEvents}
shows the sequence of events in a repository. In this case, commits are performed in
various repositories and branches. The DAG representation of the commits is shown in
figure \ref{fig:repoDAG}. Notice that the DAG loses information about the master
branch and the repository that the master branch is part of. The merge-tree view of
this DAG is visible in figure \ref{fig:repoTree}. Note that the direction of the
edges of the DAG has been inverted, instead of pointing from the child to the
ancestors, it points from the ancestor to its successors, forming a path to the
master branch. Also note that the DAG has been simplified, showing only a single
edge on the path to master for any commit.

@@

\begin{figure}[htbp]
        \centering
        \includegraphics[width=.8\columnwidth]{figures/dag.pdf}
        \caption{DAG representation of the commits represented in
                Figure~\ref{fig:repoEvents}. It loses information about what
                repository the commit is performed and through which repositories it
                has passed in its way to Master. In fact, the DAG does not even know
                what Master is.}
        \label{fig:repoDAG}
\end{figure}

\begin{figure}[htbp]
        \centering
        \includegraphics[width=\columnwidth]{figures/tree.pdf}
        \caption{Merge-tree view of the commits  represented in
                Figure~\ref{fig:repoEvents} showing the path they followed to reach
                master. In this model the successors of each commit represents the
                path followed by that commit to reach Master.}
        \label{fig:repoTree}
\end{figure}

@@

In our visualizations, we leverage the Merge-Tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already in Master,
or is part of a tree which is rooted in the merge that merged it into Master.  Each
commit, whether a merge or non-merge, has only one successor; the root of each tree
has none as it was made by Linus Torvalds directly into the master branch. Non-merge
Commits contain the metadata for the changes made. This metadata includes the files
changed, the lines added and removed from each file, the author, the date the commit
was merged into the merge that led to being merged into the kernel, the date the
commit was authored, the patch, and the commit log. Merges contain less metadata,
only storing the author of the merge, the log, the commit date, and the author date,
and potentially, changes necessary to address conflicts during the merge. The
details of the model are outlined in \cite{German2015}.

@@

\begin{itemize}
        \item Filter by searching commits by when they are merged into Master.
        \item View files edited
        \item View modules
        \item Tree viewer
\end{itemize}

\subsection{Searching by when they are merged into Master}

@@

Searching (depicted in Figure \ref{fig:search}) allows a user to filter commits and merges that are irrelevant. The search mechanism breaks down the results by
release version.  A user can further narrow down the search by \textbf{specifying a range of dates} in which such commits \textbf{were merged by Linus into
        Master, not
        when the commits were created.} This distinction is important. We have observed commits that take years
to arrive into Master after they were originally committed.

@@

\dmg{What is this commit? any commit id, or a merge into Master? Unclear.}
If providing commit ID must be specified
from the first character to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches for a
commit ID of `c26' in the 3.10 Linux kernel. We will use this commit for showing
each of the features of \tool.

@@

In the search results, the user is presented with the one-line log message preview,
the author's name and email, the date the commit was authored, and the date the
commit was last committed. The commit date and author date will usually be the same;
however, if the commit has been rebased or cherry-picked into a merge that
eventually is merged into the kernel, the commit date and authored date will be
different. We can see this in the first and third entries in figure
\ref{fig:results}.

@@

The first tab displays the full commit log (figure \ref{fig:message}). From this, a
user is able to see what they would see had they searched for the commit using git
log. This doesn't provide additional information to the other tools, but helps to
complete the functionality of \tool. The commit log provides a user with the
information about the content of the commit and who has signed-off on the commit to
ensure that it is good quality. The message for merges may contain a summary of the
commits being merged.  The information within these messages is highly variable, and
is completely dependent on the author's style. As the user moves toward the
top-level merge, the quality of these messages generally improves.

@@

The second tab is the files tab (figure \ref{fig:files}). This tab provides information on what files have been edited, how many lines were added, and how many
lines were removed in a given commit. For non-merges, this functionality is similar to the other tools available. Our tree-based design model allows us to
extend this functionality to merges by aggregating information about all the commits that are children of the merge in the merge-tree (which the other tools are
unable to show). To find the number of lines added to a file in a merge, we take the sum of the lines added to that file in each of the children of that
merge. We do the same for calculating the number of lines removed.
% This could be extended to use the patch information to determine when a line has been
% replaced rather than incrementing the lines added and removed.

@@

The modules tab (figure \ref{fig:modules}) shows the modules that are contained
within the commit. Modules are not natively recognized by git, and are not going to
be present in all repositories.  In the Linux repository, authors put the module
they are working on in the one-line preview of the log-message; for example: the log \emph{gcov: add support for FCC 4.9} has updated the \emph{gcov} module
(the coverage testing tool of the kernel). We heuristically
extract the module by taking all text in the log preview of commits until the first
colon.  Modules are logical partitions of the information in the kernel. Depending
on where the author was working, modules can be general, such as ``bluetooth'' and
``wireless'', or can be quite specific for individual hardware, such as
``ath9k\_hw'' and ``wl1251''. In a few cases, the author of a commit does not
correctly follow this format and the heuristic approach fails. As with the Files panels,
non-merge commits show their corresponding information, but for merge commits we aggregate all the modules changed
in all the commits that are part of that merge.
The output of this view is shown in Figure~\ref{fig:modules}.

Finally, we have the Tree view tab. The tree view is designed for providing easy
navigation of the commits within the merge-tree that is rooted in the current merge. It also provides a clear topological view of the merge and the submerges it includes.We have experimented with various tree designs to find a design that
allows for easy navigation and visualization of both large and small trees.  We discuss this panel in the next subsection.

@@

The merge-tree view is what makes \tool unique to other tools that inspect the DAG of a git repository. With it, a user can inspect how commits are merged
on their way to Master. We have experimented with various types of trees:

@@

The list tree viewer (figure \ref{fig:list_tree}) is in the form of nested lists,
and is designed to more closely model the tree view found in file browsers. This
tree only contains the commits and merges that are within the subtrees of the
current merge. A commit will never have any items in this tree as it is a leaf. To
accompany the tree, we include breadcrumbs at the top of the page to enable a user
to navigate both from the root to the leaves and from a leaf to the root. The last
item in the breadcrumb list is the current commit, the previous item is the parent
of the current commit, and the first item is the root merge into the kernel.

@@

To improve the visualization of the merge-tree, we first transform the merge-tree into a new tree, where each commit points to its next merge in the way to Master. However, we keep the topological order of the commits in the tree-merge as the order of the
leaves for a given merge (e.g. if merge-tree contains two commits A, B merged into C, then the simplified tree contains links B and C directly to A, but it
preserves the order of B with respect to C by showing B above C.
This allows the clustering of commits along their next merge, and avoid the space needed to
present long sequences of commits without merges in between.

The Reingold-Tilford tree\cite{Reingold1981} (Figures \ref{fig:zoomed_tree} and \ref{fig:tree}) allows the visualization and navigation
of the entire merge-tree in an intuitive representation of the tree. This illustrates a clear notion of
root and leaves, and how to navigate in either direction. Some of the merge trees are very large (figure \ref{fig:zoomed_tree}), containing
thousands of commits and merges. While the tree is capable of producing a
visualization, it becomes much more difficult to understand. For example the merge 73287a43cc79ca06629a88d1a199cd283f42456a performed by Linus Torvalds in May
1, 2013, merged 1722 non-merge commits and 91 merges. footnote{This commit can be inspected at \url{http://li.turingmachine.org/commits/73287a43cc79ca06629a88d1a199cd283f42456a}}

@@

Clicking on subtrees will cause them to collapse, only showing parts of the tree
that are of interest to the user. Furthermore, the user can zoom the tree by
scrolling the mouse wheel to see more of the topology of the tree, or to see the
details of a given part of the tree.

\dmg{do you have a figure that shows the collapsed subtrees? Try to use the same HUGE commit}

@@

Bubble trees are useful for providing a clear visualization of hierarchal
data\cite{Boardman2000}. The bubble tree (figure \ref{fig:bubble_tree}) provides a
very clear picture of where a commit is located in the tree hierarchy. The currently
selected commit or merge is colored red, while non-selected merges use a shade of
blue and commits use white.  The depth of the blue colouring is dependent on how
deep in the hierarchy that node is. The root is the lightest blue, and the contained
merges are progressively darker.

@@

\tool was built using Nginx as the main web server, postgresql as the dbms, and Flask as the framework for generating the dynamic content.

@@

From a developers point of view, the are two major disadvantages of the DAG model of git: a) its edges point backwards, i.e. commits point to their ancestor,
not to the commit that succeeds them in their way to be integrated; and b) the DAG contains many more edges that are necessary to understand how integration
happened. We addressed these two issues with the creation of the merge-tree model of the DAG of Linux. Effectively the merge-tree view recoveres the details of each merged
branch into master.

In our experience, no other git repository reaches the level of DAG complexity that Linux has. In most git repositories  every a merge into master does not
merge other merges, and most merges bring very few new commits with them. However, even in those cases, the merge-tree will provide a valuable summary of how
commits have been integrated into master, specially since the time of integration might be very different from the time the commits were created.

The biggest challenge, however, is computing the merge-tree. Our heuristic is applicable \textbf{only} to the Linux kernel, and only since July 2009 and it is
very likely it will not work for other repositories, specially those that have fast-forward commits into Master (as the majority of repositories). One way to
address this is lack of data is by monitoring at short intervals the arrival of commits into Master (as we did in \cite{German2015}, i.e.
\emph{continuously mining} a git repo). This however, requires planning.

Regarding \tool. Because it leverages the merge-tree of the kernel, it provides mechanisms and visualizations that other tools are unable to
produce.  It gives us the ability to see how commits are being merged
into the kernel, allowing us to better understand how code is integrated into the kernel.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/042dd_tree.png}
        \caption{Merge Tree View \dmg{this figure is unreadable. Any chance you can make the text bigger?}}
        \label{fig:tree_view}
\end{figure*}

Our goal was to build a tool to enable maintainers to effectively navigate and browse
the changes performed to the kernel over the period of a release.
Achieving this goal includes removing information that does not pertain to the area
of the kernel that the user is interested in. In figure \ref{fig:dag_view} and
figure \ref{fig:tree_view} we can visually compare the results returned from Gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. Note first that Gitk has no way to show that this is a merge into Master.

The log information to this merge-commit in both of these
figures is identical, but the presentation drastically changes our ability to
comprehend what we are seeing. The primary difference is the removal of irrelevant
information. In Gitk (\ref{fig:dag_view}), the visualization results include commits
and merges from other components of the kernel, while our tool (\ref{fig:tree_view})
only includes the results that are specific to the component of the kernel that we
are interested in.

@@

Using \tool many advantages over the DAG model, but there are two
drawbacks. The first drawback is that a server must query the state of the master
repository since time information is not stored by git. The second drawback is the
need to pre-compute the merge-tree of the repository.

@@

Version control systems monitor the development lifetime of software projects. This
makes the version control system vital in providing information about how a software
project is being developed. To our knowledge, we know of no git repository
visualization tool that builds a tree that maps the path a commit follows to the
master branch from the DAG provided by git. This may be because more information is
required to generate the merge-tree model than what is stored by git. However, there
has been a lot of work in providing visualizations of various repositories.

@@

Codebook, Hipikat, Fractal Figures, EPOSee, and Evolution Radar all work with data
from CVS repositories. Our goal is to provide information about git repositories,
specifically the Linux master repository. Fewer tools are available for generating
visualizations and summaries of git repositories, potentially due to the DAG model
used by git.

@@

The current industry standard tool for git repository visualization is Gitk. The
Gitk interface is built around the central DAG viewer. The DAG view displays the
commits on their respective branches, the author of the commit or merge, and the
date the commit or merge was authored. A user can select a single merge or commit
to view additional information. For both merges and commits, Gitk will present the
user with the git log. If the user selected a commit, Gitk will also present the
user with the patch information and the names of the files edited. Gitk is unable to
provide the patches and filenames information in merges, as it is unable to
aggregate commit information in merges.

@@

The tree model requires more information than what is provided by git, requiring a
central server to monitor changes to the project. This breaks the design goals of
decentralized version control systems and makes the visualization tool specific to
the project.

>>>>

        With an average of more than 900 top-level merges into the Linux kernel per
        release, many containing hundreds of commits and some containing thousands,
        maintenance of older versions of the kernel becomes nearly impossible.
        Various commercial products, such as the Android platform, run older
        versions of the kernel. Due to security, performance, and changing hardware
        needs, maintainers must understand what changes (commits) are added to the
        current version of the kernel since the last time they inspected it in order
        to make the necessary patches.

        Current tools provide information about repositories through the directed
        acyclic graph (DAG) of the repository, which is helpful for smaller
        projects. However, with the scale and number of branches in the kernel the
        DAG becomes overwhelming very quickly. Furthermore, the DAG contains every
        ancestor of every commit, while maintainers are more interested in how and
        when a commit arrives to the official Linux repository.

        In this paper, we propose the merge-tree view, a simplified transformation
        of the DAG of the Linux git repository that shows the way in which commits
        are merged into the master branch of Linux. Using the merge-tree view we
        build \tool, a tool that is designed to allow users to explore how commits
        are merged into the Linux kernel.

@@

\evantodo {
        \begin{enumerate}
                \item Check captions
        \end{enumerate}
}

Between 50k and 70k commits are added to the Linux kernel per version
requiring maintainers of older versions of the Linux kernel to sift through
thousands of commits and merges with tools that are unable to filter and effectively
visualize projects at the scale of the kernel. Older versions of the kernel are used
in embedded systems and mobile phones; for security purposes, performance needs, and
changing hardware requirements, maintainers must be able to understand the changes
being made in the current version of the kernel in order to produce the necessary
patches for the older versions of the kernel. Tools like Gitk use a directed acyclic
graph (DAG) model of the repository, showing all commits and merges in chronological
order by when the commit was authored, not by when it arrived in the official Linux
repository.

This representation works in smaller projects; it enables users to see when changes
are made, when these changes are merged, how each branch is interacting, and the
point where a branch forks from the master branch. In large modular projects, like
the Linux kernel, the DAG becomes a mess of merges and commits
(Figure~\ref{fig:gitk}) losing its visual meaning. In some cases, the Linux kernel
is simply too large for the system to generate a visualization; Github provides a
DAG view for many projects, but is unable to display the visualization for projects
at the scale of the Linux of the kernel (Figure~\ref{fig:gitfail}).  Between 60 and
70k new commits are created for the Linux project every year; According to our
previous work\cite{German2015}, a commit takes a median of 30 days from the time it
is authored until it arrives in the official repository. The snapshot of the kernel
tomorrow may be different than the snapshot from today, containing new commits
authored in the past; distinguishing these new commits from the commits in the
snapshot from today is not trivial.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitk.png}
        \caption{A sample DAG view of commits from Linux in Gitk. Commits point
                towards their ancestors, and there is no clear indication of the way
                the travel to reach master. In fact, neither Gitk nor Git is capable
                of showing what commits were done in master.}
        \label{fig:gitk}
\end{figure}

@@

Git uses a directed acyclic graph (DAG) as its main data model. In this model, a
commit has one or more ordered parents (ancestors), except the root commits of a
repository which do not have ancestors--Linux git repository has two such commits.
Commits are divided into merge commits, merging two or more branches, and non-merge
commits. Non-merge commits have only one parent, while merge commits have two or
more. The order of the parents matter: the first parent is the branch in which the
merge is being done, while the rest indicate the branches being merged (Git allows
merging multiple branches simultaneously). The second parent is the first branch
merged, the third parent is the second branched merged.

Once a commit is created, it is never changed. Git allows operations to alter
commits or reorder them, but it changes the commit ID in the process, effectively
making a new commit. This makes commits unable to record the traversal of merges
from the commit to the merge into the master branch.

A short example: assume the of commits represented in Figure~\ref{fig:repoEvents}
shows the sequence of events in a repository. In this case, commits are performed in
various repositories and branches. The DAG representation of the commits is shown in
Figure~\ref{fig:repoDAG}. Notice that the DAG loses information about the master
branch and the repository that the master branch is part of. The merge-tree view of
this DAG is visible in Figure~\ref{fig:repoTree}. Note that the direction of the
edges of the DAG has been inverted, instead of pointing from the child to the
ancestors, it points from the ancestor to its successors, forming a path to the
master branch. Also note that the DAG has been simplified, showing only a single
edge on the path to master for any commit.

@@

\begin{figure}[htbp]
        \centering
        \includegraphics[width=.8\columnwidth]{figures/dag.pdf}
        \caption{DAG representation of the commits represented in
                Figure~\ref{fig:repoEvents}. It loses information about what
                repository the commit is performed and through which repositories it
                has passed in its way to master. In fact, the DAG does not even know
                what master is.}
        \label{fig:repoDAG}
\end{figure}

\begin{figure}[htbp]
        \centering
        \includegraphics[width=\columnwidth]{figures/tree.pdf}
        \caption{Merge-tree view of the commits  represented in
                Figure~\ref{fig:repoEvents} showing the path they followed to reach
                master. In this model the successors of each commit represents the
                path followed by that commit to reach master.}
        \label{fig:repoTree}
\end{figure}

@@

In our visualizations, we leverage the Merge-Tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already in master,
or is part of a tree which is rooted in the merge that merged it into master.  Each
commit, whether a merge or non-merge, has only one successor; the root of each tree
has none as it was made by Linus Torvalds directly into the master branch. Non-merge
Commits contain the metadata for the changes made. This metadata includes the files
changed, the lines added and removed from each file, the author, the date the commit
was merged into the merge that led to being merged into the kernel, the date the
commit was authored, the patch, and the commit log. Merges contain less metadata,
only storing the author of the merge, the log, the commit date, and the author date,
and potentially, changes necessary to address conflicts during the merge. The
details of the model are outlined in \cite{German2015}.

@@

\begin{itemize}
        \item Filter by searching
        \item View files edited
        \item View modules
        \item Tree viewer
\end{itemize}

\subsection{Searching}

@@

Searching (depicted in Figure \ref{fig:search}) allows a user to filter commits and
merges that are irrelevant. The search mechanism breaks down the results by release
version. A user can further narrow down the search by \textbf{specifying a range of
dates} in which such commits \textbf{were merged by Linus into master, not when the
commits were created.} This distinction is important. We have observed commits that
have taken years to arrive into master after they were originally committed.

@@

If providing commit ID must be specified from the first character to the last
character. For example, the commit `c267548755a184ef97301071300c1739a564e135' is
returned when the user searches for a commit ID of `c26' in the 3.10 Linux kernel.
This commit is a non-merge commit performed, in one of the largest merge-trees of
the kernel; however, this feature will work with any commit ID.  We will use this
commit for showing each of the features of \tool.

@@

In the search results, the user is presented with the one-line log message preview,
the author's name and email, the date the commit was authored, and the date the
commit was last committed. The commit date and author date will usually be the same;
however, if the commit has been rebased or cherry-picked into a merge that
eventually is merged into the kernel, the commit date and authored date will be
different. We can see this in the first entry in Figure~\ref{fig:results}.

@@

The first tab displays the full commit log (Figure~\ref{fig:message}). From this, a
user is able to see what they would see had they searched for the commit using Git
log. This doesn't provide additional information to the other tools, but helps to
complete the functionality of \tool. The commit log provides a user with the
information about the content of the commit and who has signed-off on the commit to
ensure that it is good quality. The message for merges may contain a summary of the
commits being merged.  The information within these messages is highly variable, and
is completely dependent on the author's style. As the user moves toward the
top-level merge, the quality of these messages generally improves.

@@

The second tab is the files tab (Figure~\ref{fig:files}). This tab provides
information on what files have been edited, how many lines were added, and how many
lines were removed in a given commit. For non-merges, this functionality is similar
to the other tools available. Our tree-based design model allows us to extend this
functionality to merges by aggregating information about all the commits that are
children of the merge in the merge-tree, which other tools are unable to show. To
find the number of lines added to a file in a merge, we take the sum of the lines
added to that file in each of the children of that merge. We do the same for
calculating the number of lines removed.

% This could be extended to use the patch information to determine when a line has been
% replaced rather than incrementing the lines added and removed.

@@

The modules tab (Figure~\ref{fig:modules}) shows the modules that are contained
within the commit. Modules are not natively recognized by Git, and are not going to
be present in all repositories. In the Linux repository, authors put the module they
are working on in the one-line preview of the log-message; for example: the log
\emph{gcov: add support for FCC 4.9} has updated the \emph{gcov} module (the
coverage testing tool of the kernel). We heuristically extract the module by taking
all text in the log preview of commits until the first colon.  Modules are logical
partitions of the information in the kernel. Depending on where the author was
working, modules can be general, such as ``bluetooth'' and ``wireless'', or can be
quite specific for individual hardware, such as ``ath9k\_hw'' and ``wl1251''. In a
few cases, the author of a commit does not correctly follow this format and the
heuristic approach fails. As with the Files panels, non-merge commits show their
corresponding information, but for merge commits we aggregate all the modules
changed in all the commits that are part of that merge.  The output of this view is
shown in Figure~\ref{fig:modules}.

Finally, we have the Tree view tab. The tree view is designed for providing easy
navigation of the commits within the merge-tree that is rooted in the current merge.
It also provides a clear topological view of the merge and the submerges it
includes. We have experimented with various tree designs to find a design that
allows for easy navigation and visualization of both large and small trees. We
discuss this panel in the next subsection.

@@

The merge-tree view is what makes \tool unique to other tools that inspect the DAG
of a Git repository. With it, a user can inspect how commits are merged on their way
to the master branch. We have experimented with various types of trees:

@@

The list tree viewer (Figure~\ref{fig:list_tree}) is in the form of nested lists,
and is designed to more closely model the tree view found in file browsers. This
tree only contains the commits and merges that are within the subtrees of the
current merge. A commit will never have any items in this tree as it is a leaf. To
accompany the tree, we include breadcrumbs at the top of the page to enable a user
to navigate both from the root to the leaves and from a leaf to the root. The last
item in the breadcrumb list is the current commit, the previous item is the parent
of the current commit, and the first item is the root merge into the kernel.

@@

The Reingold-Tilford tree\cite{Reingold1981} (Figures \ref{fig:zoomed_tree} and
\ref{fig:tree}) allows the visualization and navigation of the entire merge-tree in
an intuitive representation of the tree.  This illustrates a clear notion of root
and leaves, and how to navigate in either direction. Some of the merge trees are
very large (Figure~\ref{fig:zoomed_tree}), containing thousands of commits and
merges. While the tree is capable of producing a visualization, it becomes much more
difficult to understand. For example the merge
73287a43cc79ca06629a88d1a199cd283f42456a performed by Linus Torvalds in May 1, 2013,
merged 1722 non-merge commits and 91 merges. \footnote{
        This commit can be inspected at
        \url{http://li.turingmachine.org/commits/73287a43cc79ca06629a88d1a199cd283f42456a}}

@@

The tree can be further extended to include the collapsing of merge nodes. Clicking
on merge nodes will cause them to collapse, only showing parts of the tree that are
of interest to the user.Furthermore, the user can zoom the tree by scrolling the
mouse wheel to see more of the topology of the tree, or to see the details of a
given part of the tree.

@@

Bubble trees are useful for providing a clear visualization of hierarchal
data\cite{Boardman2000}. The bubble tree (Figure~\ref{fig:bubble_tree}) provides a
very clear picture of where a commit is located in the tree hierarchy. The currently
selected commit or merge is colored red, while non-selected merges use a shade of
blue and commits use white.  The depth of the blue colouring is dependent on how
deep in the hierarchy that node is. The root is the lightest blue, and the contained
merges are progressively darker.

@@

\tool was built using Nginx as the main web server, postgresql as the DBMS, and
Flask as the framework for generating the dynamic content.

@@

From a developers point of view, the are two major disadvantages of the DAG model of
Git: a) its edges point backwards, i.e. commits point to their ancestor, not to the
commit that succeeds them on the path to being integrated; and b) the DAG contains
many more edges that are necessary to understand how integration occurred. We
addressed these two issues with the creation of the merge-tree model of the DAG of
Linux. Effectively the merge-tree view recovers the details of each merged branch
into master.

In our experience, no other Git repository reaches the level of DAG complexity that
Linux has. In most Git repositories, merges are not nested, all merges merge
directly into the master repository, and these merges only merge few commits. Even
in these simplified cases, the merge-tree can provide a valuable summary of how
commits are integrated into the master branch, specifically since the time of
integration may be very different from the time the commits were authored.

The biggest challenge, however, is computing the merge-tree. Our heuristic
\textbf{only} applies to the Linux kernel repository, and only since July 2009. It
is very likely that the heuristic will not work with other repository, specially
those with fast-forward commits into the master branch (a majority of repositories).
We can address the lack of information by monitoring the state of the repository at
short intervals as we did in \cite{German2015}. This continuous mining of the
repository requires foresight and planning.

Because \tool leverages the merge-tree model of the kernel, it provides mechanisms
and visualizations that other tools are unable to produce.It gives us the ability to
see how commits are being merged into the kernel, allowing us to better understand
how code is integrated into the kernel.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/042dd_tree.png}
        \caption{Merge Tree View \dmg{this Figure is unreadable. Any chance you can make the text bigger?}}
        \label{fig:tree_view}
\end{figure*}

Our goal was to build a tool to enable maintainers to effectively navigate and
browse the changes performed to the kernel over the period of a release.  Achieving
this goal includes removing information that does not pertain to the area of the
kernel that the user is interested in. In Figure~\ref{fig:dag_view} and
Figure~\ref{fig:tree_view} we can visually compare the results returned from Gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. Note that Gitk has no way to show or recognize that this
is a merge into the master branch.

The log information to this merge-commit in both of these figures is identical, but
the presentation drastically changes our ability to comprehend what we are seeing.
The primary difference is the removal of irrelevant information. In Gitk
(Figure~\ref{fig:dag_view}), the visualization results include commits and merges
from other components of the kernel, while our tool (Figure~\ref{fig:tree_view})
only includes the results that are specific to the component of the kernel that we
are interested in.

@@

The merge-tree model used in \tool has many advantages to the DAG model, but there
are two drawbacks. The first drawback is that a server must query the state of the
master repository since time information is not stored by Git in order to properly
construct the merge tree. The second drawback is the need to pre-compute the
merge-tree of the repository.

@@

Version control systems monitor the development lifetime of software projects. This
makes the version control system vital in providing information about how a software
project is being developed. To our knowledge, we know of no Git repository
visualization tool that builds a tree that maps the path a commit follows to the
master branch from the DAG provided by Git. This may be because more information is
required to generate the merge-tree model than what is stored by Git. However, there
has been a lot of work in providing visualizations of various repositories.

@@

Codebook, Hipikat, Fractal Figures, EPOSee, and Evolution Radar all work with data
from CVS repositories. Our goal is to provide information about Git repositories,
specifically the Linux master repository. Fewer tools are available for generating
visualizations and summaries of Git repositories, potentially due to the DAG model
used by Git.

@@

The current industry standard tool for Git repository visualization is Gitk. The
Gitk interface is built around the central DAG viewer. The DAG view displays the
commits on their respective branches, the author of the commit or merge, and the
date the commit or merge was authored. A user can select a single merge or commit
to view additional information. For both merges and commits, Gitk will present the
user with the Git log. If the user selected a commit, Gitk will also present the
user with the patch information and the names of the files edited. Gitk is unable to
provide the patches and filenames information in merges, as it is unable to
aggregate commit information in merges.

@@

The tree model requires more information than what is provided by Git, requiring a
central server to monitor changes to the project. This breaks the design goals of
decentralized version control systems and makes the visualization tool specific to
the project.
